\documentclass[12pt]{article}

\begin{document}
\title{I.O.Stu Specification}
\author{Stuart Reilly}
\maketitle
\newpage

\section{Introduction}
    This is the specification document for the I.O.Stu platform.
    The I.O.Stu platform is a centralised technique for users to request, repay and access information about their I.O.Stu.
    An I.O.Stu is a small, normally short-term, loan with minimal intrest from Stu.
    Previously, I.O.Stu's were only avalible through direct contact with Stu, with a large amount of manual work for Stu to monitor all the outstanding I.O.Stus.

\section{API}
    The I.O.Stu platfrom will provide a REST API over HTTPS.
    HTTP will not be supported by any part of the platform due to its insecurity and the widespread support for HTTPS.
    Data sent to and recieved from the API will be in the form of JSON for ease of serialision, deserialisation and human readabilty.

    \subsection{Security}
    All API endpoints will be carried out over HTTPS, with all HTTP requests returning a HTTP 308 Permanent Redirect status code, redirecting to the root HTTPS URI.
    All API endpoints excluding authentication endpoints, must provide an API token in the Authentication header, otherwise a HTTP 401 Unauthorised status code will be returned.
    

    \subsection{API Endpoints}
        \subsubsection{Request New}
        Request a new I.O.Stu.

        RESOURCE: POST /request
        HEADERS: Authorisation

\end{document}


#JWT in header for all requests, including login
#Checked by AuthProvider for all requests, return Unauth if bad
#When login, put user data in body as json